---
title: "Assignment 3"
format: html
editor: visual
---

***How to do it?***:

- Open the Quarto file of this assignment ([link](assignment3.qmd)) in Rstudio.

- Right under each **question**, insert a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question.

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.

- Publish the html file to your Githiub Page.

***Submission***: Submit the link on Github of the assignment to Canvas.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

------------------------------------------------------------------------

## Problems



1.  Create the following data frame

| Rank | Age | Name  |
|:-----|:----|:------|
| 0    | 28  | Tom   |
| 1    | 34  | Jack  |
| 2    | 29  | Steve |
| 3    | 42  | Ricky |


```{r}
df1 = data.frame(Rank = c(0, 1, 2, 3), 
           Age = c(28, 34, 29, 42),
           Name = c("Tom", "Jack", "Steve", "Ricky"))

df1
```


2.  Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://bryantstats.github.io/math421/data/us-states.csv).

```{r}
df2 = read.csv("https://bryantstats.github.io/math421/data/us-states.csv")
```


3.  Show the names of the variables in the data

```{r}
names(df2)
```

4.  How many columns and rows the data have?

```{r}
dim(df2)
```


5.  How many missing values are there? Show the missing values by columns. What variable has the most number of missing values?

```{r}
sum(is.na(df2))
colSums(is.na(df2))

print("None of the values are missing")

```


6.  What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column.

```{r}
class(df2$date)
df2$date = as.Date(df2$date)
class(df2$date)
```


7.  Capitalize the names of all the variables

```{r}
names(df2) = toupper(names(df2))
```



8.  Find the average number of cases per day. Find the maximum cases a day.

```{r}
# Group the values
daily = aggregate(CASES ~ DATE, data = df2, FUN = sum)

# Order then so you can difference
daily = daily[order(daily$DATE), ]
# Compute the difference per day where the first stays as the first value
new_daily_cases = c(daily$CASES[1], diff(daily$CASES))
mean(new_daily_cases)
max(new_daily_cases)

print("You have to get the daily difference because the data is cumulative")
```


9.  How many states are there in the data?

```{r}
length(unique(df2$STATE))
```


10. Create a new variable `weekdays` to store the weekday for each rows.

```{r}
df2$weekdays = weekdays(df2$DATE)
```


11. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
- `no_death` if there is no death that day

Find the frequency and relative frequency of `no_death` and `has_death`.

```{r}
df2$death2 = ifelse(df2$DEATHS > 0, "has_death", "no_death")

table(df2$death2)
prop.table(table(df2$death2))
```


12. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint: Use the `summary` function)

```{r}
summary(df2$DEATHS)
```


13. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3

```{r}
q1 = quantile(df2$DEATHS, 0.25)
q3 = quantile(df2$DEATHS, 0.75)

df2$death3 = ifelse(df2$DEATHS < q1, "low_death",
                     ifelse(df2$DEATHS <= q3, "mid_death", "high_death"))
```


14. Find the average cases in Rhode Island in 2021

```{r}
# Get just Rhode Island
ri = df2[df2$STATE == "Rhode Island", ]
ri = ri[order(ri$DATE), ]

daily_ri = aggregate(CASES ~ DATE, data = ri, FUN = sum)

ri$new_cases = c(daily_ri$CASES[1], diff(daily_ri$CASES))
ri_2021 = ri[format(ri$DATE, "%Y") == "2021", ]

mean(ri_2021$new_cases)
```


15. Find the median cases by weekdays in Rhode Island in 2021

```{r}
aggregate(new_cases ~ weekdays, data=ri_2021, FUN=median)
```


16. Compare the median cases in Rhode Island in June, July, August and September in 2021.

```{r}
ri_2021$months = months(ri_2021$DATE)

summer = ri_2021[ri_2021$months %in% c("June", "July", "August", "September"), ]

aggregate(new_cases ~ months, data = summer, FUN = median)
```


17. Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when


```{r}
df3 = read.csv("https://bryantstats.github.io/math421/data/titanic.csv")
```

```{r}
head(df3)
```

```{r}
str(df3)
```

```{r}
names(df3)
```

```{r}
mean(df3$Fare)
min(df3$Fare)
max(df3$Fare)
```
```{r}
table(df3$Sex)
table(df3$Survived, df3$Pclass)
```


```{r}
sum(is.na(df3$Age))
```

```{r}
colSums(is.na(df3))
```

```{r}
class(df3$Age)
```

```{r}
cor(df3$Fare, df3$Pclass)
```

```{r}
by(df3, df3$Sex, summary)
```

```{r}
df3$Rich = ifelse(df3$Fare > 100, 1, 0)
```

```{r}
library(dplyr)

df3$Wealth = case_when(
  df3$Pclass == 1  ~ "Weathly",
  df3$Pclass == 2 ~ "Moderate",
  df3$Pclass == 3  ~ "Poor"
)

print("Had to install dplyr")
```


18. In the dataset in #17, practice the follows. You can reuse the code of 17.

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

```{r}
df3$Cat_Ticket_Price <- case_when(
  df3$Fare < 50  ~ "Cheap",
  df3$Fare < 100 ~ "Moderate",
  df3$Fare < 150 ~ "Slightly Expensive",
  TRUE           ~ "Expensive"
)


```


```{r}
df3$Binary_Ticket_Price <- ifelse(
  df3$Cat_Ticket_Price %in% c("Cheap", "Moderate"),
  "Affordable",
  "Expensive"
)
```


If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](https://bryantstats.github.io/math421/data/titanic.csv)
