
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7 - Extra Credits: Practice dplyr and ggplot2"
---

Return Here: [README](.././)

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7_extra_credits.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas



```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Import the data at https://bryantstats.github.io/math421/data/ds_salaries.csv

```{r}
library("tidyverse")
df = read_csv("Data/ds_salaries.csv")
```


    The data description can be found at https://www.kaggle.com/datasets/saurabhshahane/data-science-jobs-salaries

2. Is there any column that contains NAs?

```{r}
df %>% is.na() %>% colSums()
```


3. What is the most frequent job title in the data?  

```{r}
table(df$job_title) %>% sort(decreasing = TRUE) %>% head(1)
```


4. Find the average salary data of the three most frequent job titles in the data. 

```{r}
# First find the 3 most frequent jobs
table(df$job_title) %>% sort(decreasing = TRUE) %>% head(3)

# Now filter to that and then group by and then summarize
df %>% filter(job_title %in% c("Data Scientist", "Data Engineer", "Data Analyst")) %>% group_by(job_title) %>% summarize(avg_salary = mean(salary_in_usd))
```


5. What is the job title that have the highest average salary?

```{r}
df %>% group_by(job_title) %>% summarise(avg_salary = mean(salary_in_usd)) %>% arrange(desc(avg_salary)) %>% head(1)
```


6. Which country gives the highest salary on average? 

```{r}
df %>% group_by(company_location) %>% summarise(avg_salary = mean(salary_in_usd)) %>% arrange(desc(avg_salary)) %>% head(1)
```


7. Plot five meaningful plots. All plots should have title, caption, and appropriate labels.

```{r}
library("ggplot2")
```

```{r}
df %>% ggplot() + geom_density(mapping = aes(salary_in_usd)) +
  scale_x_continuous(labels = scales::label_dollar()) + 
  labs(x="Salary", 
       y = "Density", 
       title = "Salary Densisty")

# The second line scale_x_continous is from ai and its to rescale the x values to read the actualy dollar amounts
```

```{r}
df %>% group_by(job_title) %>% summarize(avg_salary = mean(salary_in_usd)) %>%   arrange(desc(avg_salary)) %>%
  head(3) %>% ggplot() + geom_col(mapping = aes(job_title, avg_salary)) + labs(x="Jobs", 
       y = "Salary", 
       title = "Salary by Top Jobs")
```

```{r}
df %>% ggplot() +
  geom_boxplot(mapping = aes(experience_level, salary_in_usd)) +
  scale_y_continuous(labels = scales::label_dollar()) +
  labs(x = "Experience Level",
       y = "Salary",
       title = "Salary by Experience Level")
```

```{r}
df %>% ggplot() +
  geom_bar(mapping = aes(company_size)) +
  labs(x = "Company Size",
       y = "Number of Jobs",
       title = "Number of Jobs by Company Size")
```

```{r}
df %>% ggplot() +
  geom_histogram(mapping = aes(salary_in_usd)) +
  scale_x_continuous(labels = scales::label_dollar()) +
  labs(x = "Salary (USD)",
       y = "Number of Jobs",
       title = "Distribution of Salaries")
```




