
---
output: # rmarkdown::github_document
  html_document:
    theme: cerulean
    toc: true
  pdf_document: default
  word_document: default
title: "Assignment 5: Part 1"
---

Return Here: [README](.././)

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment5_part1.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**The data:** 

This assignment works with the Adult Census Data that can be downloaded at [this link.](https://bryantstats.github.io/math421/data/adult_census_missing.csv)

-------

**Questions**

1. Use `read_csv` to import the data.  Show the number of NAs for each columns.   

```{r}
library(tidyverse)
df = read_csv("Data/adult_census_missing.csv")
```


2. Using function `aggr` the VIM package to plot the number of NAs for each column. 

```{r}
library(VIM)
df %>% aggr(numbers=TRUE)
```


3. Find other forms of missing values. Hint: You can use the `table` function to check if there are suspicious categories (Unknown, for example) in a variable. What all other forms of missing values shown in the data. 

```{r}
table(df=="Unknown")
table(df=="unknown")
table(df=="Missing")
table(df=="missing")
table(df=="None")
table(df=="")
table(df==" ")
table(df=="?")
table(df=="N/A")

colSums(df=="Unknown", na.rm = 1)
colSums(df=="?", na.rm = 1)
```


4. Replace all the forms of missing values found to NA

```{r}
df = df %>% replace(df=="Unknown"|df=="?", NA)
```


5. Replot the number of NAs for each column. 

```{r}
df %>% aggr(numbers=TRUE)
```


6. Approach 1 to handle NAs: remove all rows that have any NAs. Save the dataset after removing as a different data. The original data is unchanged (still have NAs).  How many rows left after removing?

```{r}
df2 = drop_na(df)
```


7. Approach 2 to handle NAs:  Fill all the NAs with the previous or next value. (Hint: Using `fill` function).  Save the dataset after filling as a different data. The original data is unchanged (still have NAs). 

```{r}
df3 = df %>% fill(everything(), .direction = "updown")
```


8. Approach 3 to handle NAs: For numeric variable, replace the NAs by the median.  For categorical variables, replace the NAs to the majority. 

```{r}
# First check which are still NA
colSums(is.na(df))
```


```{r}
df4 = df

df4$workclass = replace_na(df4$workclass,      names(which.max(table(df4$workclass))))

df4$education = replace_na(df4$education,      names(which.max(table(df4$education))))

df4$occupation = replace_na(df4$occupation,     names(which.max(table(df4$occupation))))

df4$relationship = replace_na(df4$relationship,   names(which.max(table(df4$relationship))))

df4$sex = replace_na(df4$sex, names(which.max(table(df4$sex))))

df4$native.country = replace_na(df4$native.country, names(which.max(table(df4$native.country))))

df4$age = replace_na(df4$age, median(df4$age))
```




