---
title: "Assignment 7 - Visualization - Some aspects of ggplot2"
format: html
editor: visual
---

Return Here: [README](.././)

***How to do it?***:

- Open the Rmarkdown file of this assignment ([link](assignment7.qmd)) in Rstudio.

- Right under each **question**, insert a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question.

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.

- Publish the html file to your Githiub Page.

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

------------------------------------------------------------------------

Use the data of your own. Produce the following types of plots and comment on each plot. Plots should be meaningful. If you use the data we used in class, make sure the plots are not the same as the ones in the slides. All plots should have title, caption, appropriate labels on x and y-axis.

------------------------------------------------------------------------

```{r}
# Import the data
library("tidyverse")
library("ggplot2")
df = read_csv("Data/imdb_top_1000.csv")
df %>% names
```


1.  Make a plot using `facet_wrap` by one categorical variable (`facet_wrap(~variable1)`)

```{r}
# Want a more compressed categorical variable since there are not many
# I looked this up on the internet
df$Main_Genre = str_extract(df$Genre, "^[^,]+")
table(df$Main_Genre)
```


```{r}
df %>% filter(Main_Genre %in% c("Action", "Comedy")) %>% ggplot() + geom_point(mapping=aes(Meta_score, Gross)) + facet_wrap(~Main_Genre) + labs(x="Meta_score", 
       y = "Gross", 
       title = "Gross by Score")
```


2.  Make a plot using `facet_wrap` by two categorical variables (`facet_wrap(~variable1+variable2)`)

```{r}
df$Post_2010 = ifelse(df$Released_Year > 2010, "Post 2010", "Pre 2010")

df %>% filter(Main_Genre %in% c("Action", "Comedy")) %>% ggplot() + geom_point(mapping=aes(Meta_score, Gross)) + facet_wrap(~Main_Genre + Post_2010) + labs(x="Meta_score", 
       y = "Gross", 
       title = "Gross by Score Split on 2010")
```


3.  Make a plot using `position ='dodge'`.

```{r}
df %>% filter(Main_Genre %in% c("Horror", "Action")) %>% ggplot() + geom_bar(mapping=aes(Main_Genre, fill = factor(Post_2010)), position="dodge") + labs(x="Main_Genre", 
       y = "Count", 
       title = "Counts Split on 2010")
```


4.  Make a plot using `position ='fill'`.

```{r}
df %>% filter(Main_Genre %in% c("Horror", "Action")) %>% ggplot() + geom_bar(mapping=aes(Main_Genre, fill = factor(Post_2010)), position="fill") + labs(x="Main_Genre", 
       y = "Gross", 
       title = "Gross % by Score Split Year")
```


5.  Make a plot using `geom_col`.

```{r}
df %>% filter(Main_Genre %in% c("Horror", "Action", "Adventure")) %>% ggplot() + geom_col(mapping=aes(Main_Genre, Gross)) + labs(x="Main_Genre", 
       y = "Gross", 
       title = "Gross by Genres")
# Its a summation per each one
```


6.  Change the theme of one of your plots.

```{r}
df %>% filter(Main_Genre %in% c("Horror", "Action", "Adventure")) %>% ggplot() + geom_col(mapping=aes(Main_Genre, Gross)) + theme_dark() + labs(x="Main_Genre", 
       y = "Gross", 
       title = "Gross by Genres, Dark")
```


7.  Make a plot using combo filter + ggplot

```{r}
df %>% filter(Main_Genre %in% c("Animation", "Biography", "Action", "Horror", "Comedy")) %>% ggplot() + geom_bar(mapping=aes(Main_Genre, fill = factor(Post_2010)), position="fill") + labs(x="Main_Genre", 
       y = "Count", 
       title = "Gross % Split 2010")
```


8.  Make a plot using combo group_by + summarise + geom_col

```{r}
df %>% filter(Main_Genre %in% c("Animation", "Biography", "Action", "Horror", "Comedy")) %>% group_by(Main_Genre) %>% summarize(avg_gross = mean(Gross, na.rm = TRUE)) %>% ggplot() + geom_col(mapping=aes(Main_Genre, avg_gross)) + labs(x="Main_Genre", 
       y = "Average_Gross", 
       title = "Average Gross per Genre")
```


9.  Save a plot and put a link of the plot to your Github Webpage. To link a plot `abc.png` you just need to insert the following on the README.md

```{r}
gg = df %>% filter(Main_Genre %in% c("Animation", "Biography", "Action", "Horror", "Comedy")) %>% ggplot() + geom_bar(mapping=aes(Main_Genre, fill = factor(Post_2010)), position="fill") + labs(x="Main_Genre", 
       y = "Count", 
       title = "Gross % Split 2010")

ggsave(filename="Gross_by_Meta_Score.png", plot=gg)
```


```{r, eval=FALSE}
[Link to the plot](abc.png)
```

10. In this question, we will use the Covid19 vaccination data for the US. The data and data dictionary can be found at the below link:

- [Data](https://bryantstats.github.io/math421/data/vaccinations-by-manufacturer.csv)

```{r}
library(tidyverse)
df = read_csv('https://bryantstats.github.io/math421/data/vaccinations-by-manufacturer.csv')
```

`Geom_point` makes scatter plots, which plot two numeric (or Date) variables. A third categorical variable is often brought in for color. For example, we can compare different vaccine types used in the US by

```{r}
df %>% 
  filter(location=='United States') %>% 
  ggplot()+
  geom_point(mapping = aes(x = date, 
                                    y = total_vaccinations, 
                                    color = vaccine))
```

Do the follows.

- Use `geom_point` to compare the vaccines used by date in Argentina in 2022.

```{r}
df %>% 
  filter(location=='Argentina' & date >= "2022-01-01") %>% 
  ggplot()+
  geom_point(mapping = aes(x = date, 
                                    y = total_vaccinations, 
                                    color = vaccine))
```


- Change `geom_point` to `geom_line` in the above codes to have the corresponding line plots.

```{r}
df %>% 
  filter(location=='Argentina' & date >= "2022-01-01") %>% 
  ggplot()+
  geom_line(mapping = aes(x = date, 
                                    y = total_vaccinations, 
                                    color = vaccine))
```


11. (Using the same dataset as in 10.) Sometime we need to do some calculations on the data before plotting. For example, the below codes is to compare the total vaccines (including all types of vaccines) by date between the US and the EU

```{r}
# the total vaccines (including all types of vaccines) by date
d1 <- df %>% 
  filter(location %in% c('United States', 'European Union')) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE))

# Plot
d1 %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))
```

Notice that the above codes could be piped in one

```{r, eval=FALSE}
df %>% 
  filter(location %in% c('United States', 'European Union')) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))
```

Do the follows.

- Use `geom_point` compare the total vaccines (including all types of vaccines) by date between countries/regions in Asia

```{r}
df %>% 
  filter(location %in% c("Hong Kong", "Japan", "Nepal", "South Korea")) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))
```


- Use `geom_point` compare the total vaccines (including all types of vaccines) by date between countries/regions in South America in 2021


```{r}
df %>% 
  filter(location %in% c("Argentina", "Chile", "Ecuador", "Peru", "Uruguay")) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot()+
  geom_point(mapping=aes(x=date, 
                         y=total_vac2, 
                         color=location))
```




