
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 4 - Extra Credits"
---

Return Here: [README](.././)

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment4_extra_credits.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- Notice that if there is `eval=FALSE` in the first line of the code chunk, the chunk will not be execute.

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

This assignment works with the [IMDB Top 1000 data](../data/imdb_top_1000.csv).  Find out more information about this data at [this link](https://www.kaggle.com/datasets/harshitshankhdhar/imdb-dataset-of-top-1000-movies-and-tv-shows).  Import the data and answer the following questions. 

```{r}
library(tidyverse)
df = read_csv("Data/imdb_top_1000.csv")
```


1. List all the names of the columns of the data

```{r}
df %>% names
```


2. Which movies have the highest money earned (Gross)?

```{r}
df %>% group_by(Series_Title) %>% summarize(mean_gross = mean(Gross, na.rm=TRUE)) %>% arrange(desc(mean_gross))
```


3. What is the lowest rating (IMDB_Rating)?  List five movies have this lowest rating.

```{r}
min(df$IMDB_Rating, na.rm=TRUE)

df %>%
  filter(IMDB_Rating == min(IMDB_Rating, na.rm = TRUE)) %>%
  select(Series_Title, IMDB_Rating) %>%
  head(5)
```


4. Which year have the most number of movies released in the list?  What is the total of money earned on that year?

```{r}
df %>% count(Released_Year) %>% arrange(desc(n)) %>% head(1)

df %>% filter(Released_Year==2014) %>% summarize(total_gross = sum(Gross, na.rm=TRUE))
```


5. What is the total money earned per movies on average?

```{r}
df %>% summarize(mean(Gross, na.rm=TRUE))
```


6. Calculate the average number of votes by year. Calculate the average number of votes of movies that have IMDB rating greater than 9.

```{r}
df %>% group_by(Released_Year) %>% summarize(avg_votes = mean(No_of_Votes, na.rm=TRUE))

df %>% filter(IMDB_Rating > 9) %>% summarize(avg_votes = mean(No_of_Votes, na.rm=TRUE))
```


7. Calculate the average Meta score in 2020 of movies that have number of votes in the third quartile. 

```{r}
q2 <- quantile(df$No_of_Votes, 0.50, na.rm = TRUE)
q3 <- quantile(df$No_of_Votes, 0.75, na.rm = TRUE)

df %>% filter(Released_Year == 2020, No_of_Votes > q2, No_of_Votes <= q3) %>% summarize(avg_meta = mean(Meta_score, na.rm=TRUE))
```


8. (Optional - Challenging). The current `Runtime` variable is not a numeric. Use the `str_remove` function to remove ` min` from the variables then use `as.numeric` to convert the variable to numeric. Calculate the average running time in the 2010s. Calculate the correlation between running time and rating (adding `use="complete.obs"` in the `cor` function to ignore the missing values).  

```{r}
df <- df %>%
  mutate(Runtime = as.numeric(str_remove(Runtime, " min")))

df %>%
  filter(as.numeric(Released_Year) >= 2010,
         as.numeric(Released_Year) <= 2019) %>%
  summarize(avg_runtime = mean(Runtime, na.rm = TRUE))

cor(df$Runtime, df$IMDB_Rating, use = "complete.obs")
```


9. We can use `select_if` to select columns satisfying a condition and use `summarise_if` to do calculation on columns satisfying a condition.  Try the follows to understand these functions. 

```{r,eval=FALSE}
# Select only character columns
df %>% select_if(is.character)

# Calculate the median of all numeric columns
df %>% summarise_if(is.numeric, mean, na.rm=TRUE)
```


10. Implement the follows functions or combos. Drawing a comment or summary from each calculation. The codes in this question should be different from the codes used in other questions.

- select
- filter
- mutate
- summarise
- arrange
- count
- count + arrange
- filter + count + arrange
- group_by + summarise
- filter + group_by + summarise
- filter + group_by + summarise + arrange


1. Show data in Rating column

```{r}
df %>% select(IMDB_Rating)
```

2. Show data for Covid year

```{r}
df %>% filter(Released_Year==2020)
```

3. Turn Gross into millions

```{r}
df %>% mutate(Gross_millions = Gross/1000000)
```

4. Summarize Gross

```{r}
df %>% summarize(avg_gross = mean(Gross, na.rm=TRUE))
```

5. Arrange movies by runtime

```{r}
df %>% arrange(desc(Runtime))
```

6. Count the number of movies, or rows in the data

```{r}
df %>% count()
```

7. Count the number of movies per year

```{r}
df %>% count(Released_Year) %>% arrange(desc(n))
```

8. Count the number of movies in the 2010's

```{r}
df %>% filter(Released_Year >= 2010, Released_Year <= 2019) %>% count(Released_Year) %>% arrange(desc(n))
```

9. Groupby year get total gross

```{r}
df %>% group_by(Released_Year) %>% summarize(total_gross = sum(Gross, na.rm=TRUE))
```

10. Filter to 2010's groupby year get total gross

```{r}
df %>% filter(Released_Year >= 2010, Released_Year <= 2019) %>% group_by(Released_Year) %>% summarize(total_gross = sum(Gross, na.rm=TRUE))
```


10. Filter to 2010's groupby year get total gross sort descending

```{r}
df %>% filter(Released_Year >= 2010, Released_Year <= 2019) %>% group_by(Released_Year) %>% summarize(total_gross = sum(Gross, na.rm=TRUE)) %>% arrange(desc(total_gross))
```

